---
title: "Chudi Thesis"
author: "Chudi Gong"
date: "17/06/2020"
geometry: margin=1.5cm
output: pdf_document
bibliography: references.bib
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tinytex)
library(vctrs)
library(dplyr)
library(magrittr)
library(ggplot2)
library(readr)
library(tidyr)
library(RColorBrewer)
library(papaja)
library(MOTE)
library(MESS)
getwd()
myround_p <- function(x, digits = 3){
  if (x < 10^-digits) return(paste('<', 10^-digits))
  paste('=', myround(x, digits))
}

```
# 1.Introduction 

# 2.Method 

```{r include=FALSE}
#open file
Data <- read.csv("Data.csv")

#creat a new file with only includedtrials 
Data_Valid <- Data %>% 
  #Filter out the excluded trials 
  filter(inclusion==1) %>%
  filter(! response=="NaN") %>%
  mutate(rt=response_time*1000) %>%
  mutate(log_rt=log(rt))
Data_Valid 

#get number of subjects
Behavioural_subj <- Data_Valid %>% 
  group_by(subj_id) %>%
  summarise(totaltrials=(count=n()))
Behavioural_subj
no_subj <- nrow(Behavioural_subj)

Data_Det <- Data_Valid %>% 
  #only include detection 
  filter(task=="Detection")
Data_Det

Data_Dis <- Data_Valid %>% 
  #only include detection 
  filter(task=="Discrimination")
Data_Dis

Data_Til<- Data_Valid %>% 
  #only include detection 
  filter(task=="Tilt")
Data_Til

#count the total no of trials for each task for each participant
total_trials <- Data_Valid %>%
  group_by(subj_id, task) %>%
  summarise(totaltrials=(count=n()))
total_trials

#get the number of trials for each participants where they responded 1, p for positive
p_trials <- Data_Valid %>%
  group_by(subj_id, task) %>%
  filter(stimulus=="1") %>%
  summarise(p_trials=(count=n()))
p_trials

#count no. of correct trials for each task for each participant
individual_trials <- Data_Valid %>% 
  #group by ID, type of task and accuracy
  group_by(subj_id, task, accuracy) %>% 
  #count number of correct/incorrect/NAH trials 
  summarize(no_trials=(count = n())) %>%
  #combine with the total data frame
  inner_join(total_trials, by = c ("subj_id","task")) %>%
  mutate(proportion = no_trials / totaltrials)
individual_trials

#display accuracy 
individual_accuracy <- individual_trials %>%
  filter(accuracy==1) %>%
  rename(correct=proportion)
individual_accuracy

```

# 3.Results
## 3.1

```{r, echo=FALSE, message=FALSE}
number_ticks <- function(n) {function(limits) pretty(limits, n)}
data <- individual_accuracy
ggplot(data, mapping = aes(x= task, y=correct)) + ylim(0.4, 1) +labs(title="Fig.1 Mean accuracy across three tasks", y="mean accuracy")+ theme_classic() +
   geom_boxplot()+ geom_jitter(position=position_jitter(width=.1, height=0), alpha=0.3, size=4) + scale_y_continuous(breaks=number_ticks(6), limits=c(0.4, 1)) + geom_hline(yintercept=0.5, linetype="dashed", color = "black") + theme(plot.title = (element_text(color = "black", size = 12, face = "italic")))

```


```{r, include=FALSE}
#display accuracy for each task 
task_accuracy <- individual_accuracy %>%
  group_by(task) %>%
  summarise(mean(correct))
task_accuracy

getmean <- task_accuracy$'mean(correct)'
names(getmean) <-task_accuracy$task

#ANOVA comparing task performance 
aov.Mean_accuracy <- aov(correct~task,data=individual_accuracy)

summary(aov.Mean_accuracy)
p1 <- summary(aov.Mean_accuracy)[[1]][["Pr(>F)"]][[1]]
F1 <- summary(aov.Mean_accuracy)[[1]][["F value"]][[1]]

#############################
#calculating HIT and FA rate
#############################

#combine with the ptrials data frame
trials <- Data_Valid %>% 
  #group by ID, type of task and accuracy
  group_by(subj_id, task, accuracy, response) %>% 
  #count number of correct/incorrect/NAH trials 
  summarize(no_trials=(count = n())) %>%
  inner_join(p_trials, by = c ("subj_id","task"))
trials

hit_detect <- individual_trials %>% 
  filter(task=="Detection", accuracy=="1") %>%
  summarize(no_trials=(count = n()))
hit_detect

#calculating HIT FA rate for detection
hit_det <- trials %>% 
  filter(task=="Detection", response== "1", accuracy=="1") %>%
  mutate(hit_rate = no_trials / p_trials) %>%
  mutate(z_hit= qnorm(hit_rate))
hit_det

det_hit <- mean(hit_det$hit_rate)

fa_det <- trials %>% 
  filter(task=="Detection", response== "1", accuracy=="0") %>%
  mutate(fa_rate = no_trials / p_trials) %>%
  mutate(z_fa= qnorm(fa_rate)) %>%
  inner_join(hit_det, by = c ("subj_id","task", "response", "p_trials")) %>%
  mutate(dprime= z_hit-z_fa)
fa_det

det_fa <- mean(fa_det$fa_rate)

#calculating HIT FA for discrimination
hit_dis <- trials %>% 
  filter(task=="Discrimination", response== "1", accuracy=="1") %>%
  mutate(hit_rate = no_trials / p_trials) %>%
  mutate(z_hit= qnorm(hit_rate))
hit_dis

fa_dis<- trials %>% 
  filter(task=="Discrimination", response== "1", accuracy=="0") %>%
  mutate(fa_rate = no_trials / p_trials)%>%
  mutate(z_fa= qnorm(fa_rate)) %>%
  inner_join(hit_dis, by = c ("subj_id","task", "response", "p_trials")) %>%
  mutate(dprime= z_hit-z_fa)
fa_dis

#calculating HIT FA rate for tilt
hit_til <- trials %>% 
  filter(task=="Tilt", response== "1", accuracy=="1") %>%
  mutate(hit_rate = no_trials / p_trials) %>%
  mutate(z_hit= qnorm(hit_rate))
hit_til

til_hit <- mean(hit_til$hit_rate)

fa_til<- trials %>% 
  filter(task=="Tilt", response== "1", accuracy=="0") %>%
  mutate(fa_rate = no_trials / p_trials) %>%
  mutate(z_fa= qnorm(fa_rate)) %>%
  inner_join(hit_til, by = c ("subj_id","task", "response", "p_trials")) %>%
  mutate(dprime= z_hit-z_fa) 
fa_til
til_fa <- mean(fa_til$fa_rate)

#merge together 
d_prime <- rbind(fa_det, fa_dis, fa_til)

#d values for each task
d_det <- mean(fa_det$dprime)
d_dis <- mean(fa_dis$dprime)
d_til <- mean(fa_til$dprime)

#ANOVA Calculation for d prime
aov.d <- aov(dprime~task, data=d_prime)
summary(aov.d)
p2 <- summary(aov.d)[[1]][["Pr(>F)"]][[1]]
F2<- summary(aov.d)[[1]][["F value"]][[1]]

###########################
#response bias calculation
###########################
response <- Data_Valid %>% 
  #group by ID, type of task and accuracy
  group_by(subj_id,task, response) %>% 
  #count number of correct/incorrect/NAH trials 
  summarize(no_trials=(count = n())) %>%
  #combine with the total data frame
  inner_join(total_trials, by = c ("task","subj_id")) %>%
  mutate(probability = no_trials / totaltrials)
response

#response bias for detection
det_resp <- response %>%
  filter(task=="Detection") %>%
  filter(response=="1")
det_resp

det_bias <- mean(det_resp$probability)
sd_bias1 <- sd(det_resp$probability)
detection<- (rnorm(no_subj, mean = det_bias, sd = sd_bias1))
t.test(detection, mu = 0.5) # Ho: mu = 0.5

#response bias for discrimination
dis_resp <- response %>%
  filter(task=="Discrimination") %>%
  filter(response=="1")
dis_resp

dis_bias <- mean(dis_resp$probability)
sd_bias2 <- sd(dis_resp$probability)
discrimination<- (rnorm(no_subj, mean = dis_bias, sd = sd_bias2))
t.test(discrimination, mu = 0.5) # Ho: mu = 0.5

#response bias for tilt recognition
til_resp <- response %>%
  filter(task=="Tilt") %>%
  filter(response=="1")
til_resp

til_bias <- mean(til_resp$probability)
sd_bias3 <- sd(til_resp$probability)
tilt<- (rnorm(no_subj, mean = til_bias, sd = sd_bias3))
t.test(tilt, mu = 0.5) # Ho: mu = 0.5

#####################
#calculating rt
#####################
rt <- Data_Valid %>%
  group_by(subj_id, task, response, accuracy) %>%
  summarise(median(rt)) %>%
  rename("median_rt"="median(rt)")
rt

#calculating median rt for correct and incorrect trials
rt_accuracy <- rt %>%
  group_by(accuracy) %>%
  summarise(median(median_rt)) %>%
  rename("median_rt"="median(median_rt)") 
rt_accuracy

rt_accuracy$accuracy[rt_accuracy$accuracy=="0"]<-"incorrect"
rt_accuracy$accuracy[rt_accuracy$accuracy=="1"]<-"correct"

#calling out median rt for correct and incorrect trials
getmedian <- rt_accuracy$'median_rt'
names(getmedian) <-rt_accuracy$accuracy

#calling out quantiles of rt for correct and incorrect trials
correct_trials <- rt %>%
  filter(accuracy==1)
correct_trials

incorrect_trials <- rt %>%
  filter(accuracy==0)
incorrect_trials 

qt1_correct <- quantile(correct_trials$median_rt, c(.25)) 
qt3_correct <- quantile(correct_trials$median_rt, c(.75))
qt1_incorrect <- quantile(incorrect_trials$median_rt, c(.25)) 
qt3_incorrect <- quantile(incorrect_trials$median_rt, c(.75))

#get t test results detection, discrimination and tilt 
tdet <-t.test(log_rt~response, mu=0, alt="two.sided", conf=0.95,var.equal=TRUE, data=Data_Det)$statistic
p.det <- t.test(log_rt~response, mu=0, alt="two.sided",conf=0.95,var.equal=TRUE, data=Data_Det)$p.value

tdis <-t.test(log_rt~response, mu=0, alt="two.sided", conf=0.95,var.equal=TRUE,data=Data_Dis)$statistic
p.dis <-t.test(log_rt~response, mu=0, alt="two.sided", conf=0.95,var.equal=TRUE,data=Data_Dis)$p.value

ttil <-t.test(log_rt~response, mu=0, alt="two.sided", conf=0.95,var.equal=TRUE,data=Data_Til)$statistic
p.til <-t.test(log_rt~response, mu=0, alt="two.sided",conf=0.95,var.equal=TRUE,data=Data_Til)$p.value

```
Performan across the three tasks, detection (accuracy= `r apa(unname(getmean['Detection']), 2, T)`, d'= `r apa(d_det, 2, T)`),  discrimination (accuracy= `r apa(unname(getmean['Discrimination']), 2, T)`, d'= `r apa(d_dis, 2, T)`) and tilt recognition (accuracy = `r apa(unname(getmean['Tilt']), 2, T)`, d'= `r apa(d_til, 2, T)`) was similar. An one-way ANOVA failed to detect a significant difference between the accuracy of these threee tasks (F= `r apa(F1, 2, T)`, p= `r apa(p1, 2, T)`, ) and d' (F= `r apa(F2, 2, T)`, p= `r apa(p2, 2, T)`).

The probability of responding YES in detection was `r format(round(print(det_bias), 2), nsmall = 2)` (± `r apa(sd_bias1, 2, T)`), and was significantly different from 0.5 (ADD T TEST RESULTS). The probability of responding CLOCKWISE was `r apa(dis_bias, 2, T)` (± `r apa(sd_bias2, 2, T)`) and was not significantly different from 0.5. For the tilt recognition task, the probability of responding TILTED was (`r apa(til_bias, 2, T)` ± `r apa(sd_bias3, 2, T)`).

Response time was faster for correct response (1st quartile= `r apa(qt1_correct, 2, T)`, median= `r apa(unname(getmedian['correct']), 2, T)`, 3rd quartile= `r apa(qt3_correct, 2, T)` milliseconds) than incorrect responses (1st quartile= `r apa(qt1_incorrect, 2, T)`, median= `r apa(unname(getmedian['incorrect']), 2, T)`, 3rd quartile= `r apa(qt3_incorrect, 2, T)` milliseconds). A one-way analysis of variance failed to detect a significant overall effect of responses type in detection (YES vs. NO, t=`r apa(tdet, 2, T)` p=`r apa(p.det, 2, T)` ), discrimination (CLOCKWISE vs. ANTICLOCKWISE, t=`r apa(tdis, 2, T)`, p= `r apa(p.dis, 2, T)`) and tilt recognition (VERTICAL vs. TILTED, t=`r apa(ttil, 2, T)`, p= `r apa(p.til, 2, T)`) on response time. 

```{r include=FALSE}
#mean confidence frequency 
confidence_distribution <- Data_Valid %>%
  group_by(task,confidence,response) %>%
  summarise(no_trials=(count=n())) %>%
  mutate(frequency = no_trials / no_subj)
confidence_distribution

#creat a new file with only detection 
confidence_detection <- confidence_distribution %>% 
  #only include detection 
  filter(task=="Detection")
confidence_detection

confidence_detection$response[confidence_detection$response=="0"] <- "No"
confidence_detection$response[confidence_detection$response=="1"] <- "Yes"

#creat a new file with only discrimination 
confidence_discrimination <- confidence_distribution %>% 
  #only include discrimination 
  filter(task=="Discrimination") 
confidence_discrimination
confidence_discrimination$response[confidence_discrimination$response=="0"]<-"Anticlockwise"
confidence_discrimination$response[confidence_discrimination$response=="1"]<-"Clockwise"

#creat a new file with only tilt recognition 
confidence_tilt <- confidence_distribution %>% 
  #only include til recognition 
  filter(task=="Tilt") 
confidence_tilt

confidence_tilt$response[confidence_tilt$response=="0"] <-"Vertical"
confidence_tilt$response[confidence_tilt$response=="1"] <-"Tilted"
number_ticks <- function(n) {function(limits) pretty(limits, n)}

#SE calculation  (the standard deviation divided by the square root of the sample size)
#se <- function(x) sqrt(var(x)/length(x))
pd <- position_dodge(0.5) # move them .05 to the left and right
ci <- se(confidence_detection$frequency)
```
&nbsp;

&nbsp;

# 2.Confidence distributions
&nbsp;

&nbsp;

```{r echo=FALSE}
#plot the frequency of confidence ratings for detection
cbPalette <- c("#e41a1c", "#377eb8")
confidence_det <- ggplot(confidence_detection, mapping = aes(x = confidence, y= frequency, fill= response)) +
  geom_bar(stat="identity", width = 0.65, position = position_dodge(width = 0.7))+ scale_fill_manual(values=cbPalette) + theme_classic() + labs(title="Fig.2 Detection", y="frequency")+ scale_x_continuous(breaks=number_ticks(6)) + geom_errorbar(aes(ymin=frequency-ci, ymax=frequency+ci), width=.1, position=pd) +ylim(0,30)+
  theme(plot.title = (element_text(color = "black", size = 12, face = "italic")))
confidence_det
```
&nbsp;

&nbsp;

```{r echo=FALSE}
cii <- se(confidence_discrimination$frequency)
caPalette <- c("#4daf4a", "#984ea3")
#plot the frequency of confidence ratings for discrimination
confidence_dis <- ggplot(confidence_discrimination, mapping = aes(x = confidence, y= frequency, fill=response)) +
  geom_bar(stat="identity", width = 0.65, position = position_dodge(width = 0.7))+ scale_fill_manual(values=caPalette) + theme_classic() + labs(title="Fig.3 Discrimination", y="frequency")+ scale_x_continuous(breaks=number_ticks(6)) +
  geom_errorbar(aes(ymin=frequency-cii, ymax=frequency+cii), width=.1, position=pd) +ylim(0,30)+
  theme(plot.title = (element_text(color = "black", size = 12, face = "italic")))
confidence_dis
```
&nbsp;

&nbsp;

```{r echo=FALSE}
ciii <- se(confidence_tilt$frequency)
ccPalette <- c("#999999","#f781bf")
#plot the frequency of confidence ratings for tilt recognition 
confidence_til<- ggplot(confidence_tilt, mapping = aes(x = confidence, y= frequency, fill= response)) +
  geom_bar(stat="identity", width = 0.65, position = position_dodge(width = 0.7))+ scale_fill_manual(values=ccPalette) + theme_classic() + labs(title="Fig.4 Tilt recognition", y="frequency")+ scale_x_continuous(breaks=number_ticks(6)) +
  geom_errorbar(aes(ymin=frequency-ciii, ymax=frequency+ciii), width=.1, position=pd)+ ylim(0,30) +
  theme(plot.title = (element_text(color = "black", size = 12, face = "italic")))
confidence_til
```

```{r include=FALSE}
det <- Data_Valid %>%
  filter(task=="Detection") 
det

dis <- Data_Valid %>%
  filter(task=="Discrimination") 
dis

til <- Data_Valid %>%
  filter(task=="Tilt") 
til

p1 <- t.test(confidence~response, mu=0, alt="two.sided", conf=0.95, data = det)$p.value
t1 <- t.test(confidence~response, mu=0, alt="two.sided", conf=0.95, data = det)$statistic
p3 <- t.test(confidence~response, mu=0, alt="two.sided", conf=0.95, data = til)$p.value
t3 <- t.test(confidence~response, mu=0, alt="two.sided", conf=0.95, data = til)$statistic
```
Within detection, a significant difference in mean confidence was observed between YES (target present) and NO (target absent) responses (see Fig.4 above) (t=`r apa(t1, 2, T)`, p = `r myround_p (apa(p1, 2, T))`) , such that participants are more confident in their YES responses than NO response and a statistical significance was also observed in the tilt recognition task between TILTED and Vertical response (t=`r apa(t3, 2, T)`, p = `r myround_p(apa(p3, 2, T))`).

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

&nbsp;

# 3.Type 1 ROC curves

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.5}
#Type 1 ROC preparation
#get the total number of trials for each type of stimuli
sti <- Data_Valid %>%
  group_by(subj_id, task, stimulus) %>%
  summarise(total_sti_trials=(count=n())) 
sti

#get the total number of trials for correct and incoccrect trials
acc <- Data_Valid %>%
  group_by(subj_id, task, accuracy, response) %>%
  summarise(total_acc_trials=(count=n())) 
acc

conf_prob_acc <- Data_Valid %>%
  group_by(subj_id, task, stimulus, response, accuracy, confidence) %>%
  summarise(no_trials=(count=n())) %>%
  inner_join(acc, by = c ("subj_id","task", "response","accuracy")) %>%
  mutate(prob_acc= no_trials/total_acc_trials)
conf_prob_acc

conf_prob <- Data_Valid %>%
  group_by(subj_id, task, stimulus, response, accuracy, confidence) %>%
  summarise(no_trials=(count=n())) %>%
  inner_join(sti, by = c ("subj_id","task", "stimulus")) %>%
  mutate(prob= no_trials/total_sti_trials) %>%
  inner_join(conf_prob_acc, by = c ("subj_id","task", "stimulus", "response", "confidence","accuracy", "no_trials"))
conf_prob

#Detection peparation
#include only trials for detection
conf_det <- conf_prob %>%
  filter(task=="Detection")
conf_det

#subset trials which no stimulus was shown to participants
conf_det_0 <- subset(conf_det, stimulus=="0", select=c(confidence, response, prob))
conf_det_0 <- conf_det_0[order(conf_det_0[,1,2]),]

#count the probability of participants make response 1/0 at each confidence rating in no stimulus trials
confdet0 <- conf_det_0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob/no_subj)
confdet0

#round probability to 5 decimal places (for later calculation)
confdet0[,'prob']=round(confdet0[,'prob'],5)

#subset trials which stimulus was shown to participants
conf_det_1 <- subset(conf_det, stimulus=="1", select=c(confidence, response, prob))
conf_det_1 <- conf_det_1[order(conf_det_1[,1,2]),]

#count the probability of participants make response 1/0 at each confidence rating in yes stimulus trials
confdet1 <- conf_det_1%>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob/no_subj)
confdet1

#round probability to 5 decimal places (for later calculation)
confdet1[,'prob']=round(confdet1[,'prob'],5)

#separate no stimulus trials based on response type
confdet0_1 <- confdet0 %>%
  filter(response=="1")
confdet0_1
confdet0_0 <- confdet0 %>%
  filter(response=="0")
confdet0_0
#order noresponse with descending confidence rating and yes response with ascending confidence rating
confdet0_1 <- confdet0_1[order(-confdet0_1$confidence),]
confdet0_0 <- confdet0_0[order(confdet0_0$confidence),]

#rebind no stimulus trials together
confdet0 <- rbind(confdet0_1,confdet0_0)

#get the cumulative value 
confdet0[,'prob0']=cumsum(confdet0[,'prob']) 

#separate yes stimulus trials based on response type
confdet1_0 <- confdet1 %>%
  filter(response=="0")
confdet1_0
confdet1_1 <- confdet1 %>%
  filter(response=="1")
confdet1_1

#order no response with descending confidence rating and yes response with ascending confidence rating
confdet1_1 <- confdet1_1[order(-confdet1_1$confidence),]
confdet1_0 <- confdet1_0[order(confdet1_0$confidence),]

#rebind yes stimulus trials
confdet1 <- rbind(confdet1_1,confdet1_0)

#get the cumulative value 
confdet1[,'prob1']=cumsum(confdet1[,'prob']) 

#get the probability column in reorganized yes and no stimulus df
confdet1 <- select(confdet1, 1,4)
confdet0 <- select(confdet0, 1,4)

#assign an id to the df
confdet1$ID <- seq.int(nrow(confdet1))
confdet0$ID <- seq.int(nrow(confdet0))

conf_det_sti0 <- inner_join(confdet0,confdet1, by= c("ID"))

#Discrimination peparation
conf_dis <- conf_prob %>%
  filter(task=="Discrimination")
conf_dis

conf_dis_0 <- subset(conf_dis, stimulus=="0", select=c(confidence, response, prob))
conf_dis_0 <- conf_dis_0[order(conf_dis_0[,1,2]),]

confdis0 <- conf_dis_0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob/no_subj)
confdis0

conf_dis_1 <- subset(conf_dis, stimulus=="1", select=c(confidence, response, prob))
conf_dis_1 <- conf_dis_1[order(conf_dis_1[,1,2]),]

confdis1 <- conf_dis_1%>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob/no_subj)
confdis1

confdis0[,'prob']=round(confdis0[,'prob'],5)
confdis1[,'prob']=round(confdis1[,'prob'],5)

confdis0_1 <- confdis0 %>%
  filter(response=="1")
confdis0_1

confdis0_0 <- confdis0 %>%
  filter(response=="0")
confdis0_0

confdis0_1 <- confdis0_1[order(-confdis0_1$confidence),]
confdis0_0 <- confdis0_0[order(confdis0_0$confidence),]

confdis0 <- rbind(confdis0_1,confdis0_0)
confdis0[,'prob0']=cumsum(confdis0[,'prob']) 

confdis1_0 <- confdis1 %>%
  filter(response=="0")
confdis1_0

confdis1_1 <- confdis1 %>%
  filter(response=="1")
confdis1_1

confdis1_1 <- confdis1_1[order(-confdis1_1$confidence),]
confdis1_0 <- confdis1_0[order(confdis1_0$confidence),]


confdis1 <- rbind(confdis1_1,confdis1_0)

confdis1[,'prob1']=cumsum(confdis1[,'prob']) 

confdis1 <- select(confdis1, 1,4)
confdis0 <- select(confdis0, 1,4)

confdis1$ID <- seq.int(nrow(confdis1))
confdis0$ID <- seq.int(nrow(confdis0))

conf_dis_sti0 <- inner_join(confdis0,confdis1, by= c("ID"))

#Tilt peparation
conf_til <- conf_prob %>%
  filter(task=="Tilt")
conf_til

conf_til_0 <- subset(conf_til, stimulus=="0", select=c(confidence, response, prob))
conf_til_0 <- conf_til_0[order(conf_til_0[,1,2]),]

conftil0 <- conf_til_0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob/no_subj)
conftil0

conftil0[,'prob']=round(conftil0[,'prob'],5)

conftil0_1 <- conftil0 %>%
  filter(response=="1")
conftil0_1

conftil0_0 <- conftil0 %>%
  filter(response=="0")
conftil0_0

conftil0_1 <- conftil0_1[order(-conftil0_1$confidence),]
conftil0_0 <- conftil0_0[order(conftil0_0$confidence),]

conftil0 <- rbind(conftil0_1,conftil0_0)
conftil0[,'prob0']=cumsum(conftil0[,'prob']) 

conf_til_1 <- subset(conf_til, stimulus=="1", select=c(confidence, response, prob))
conf_til_1 <- conf_til_1[order(conf_til_1[,1,2]),]

conftil1 <- conf_til_1%>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob/no_subj)
conftil1

conftil1[,'prob']=round(conftil1[,'prob'],5)

conftil1_0 <- conftil1 %>%
  filter(response=="0")
conftil1_0

conftil1_1 <- conftil1 %>%
  filter(response=="1")
conftil1_1

conftil1_1 <- conftil1_1[order(-conftil1_1$confidence),]
conftil1_0 <- conftil1_0[order(conftil1_0$confidence),]


conftil1 <- rbind(conftil1_1,conftil1_0)

conftil1[,'prob1']=cumsum(conftil1[,'prob']) 

conftil1 <- select(conftil1, 1,4)
conftil0 <- select(conftil0, 1,4)

conftil1$ID <- seq.int(nrow(conftil1))
conftil0$ID <- seq.int(nrow(conftil0))

conf_til_sti0 <- inner_join(conftil0,conftil1, by= c("ID"))
#################################### 
# Plotting type 1 ROC
####################################
roc1_det <- ggplot(data=conf_det_sti0, aes(x=prob0, y=prob1)) +
  geom_line() +
  geom_point() + labs(title="Fig.5 Type 1 ROC Detection", x= "FAR", y="HR")+ 
  scale_x_continuous(breaks=number_ticks(6)) + scale_y_continuous(breaks=number_ticks(6)) +
  theme_classic() 
roc1_det

roc1_dis <- ggplot(data=conf_dis_sti0, aes(x=prob0, y=prob1)) +
  geom_line() +
  geom_point() + labs(title="Fig.6 Type 1 ROC Discrimination", x= "FAR", y="HR")+ 
  scale_x_continuous(breaks=number_ticks(6)) + scale_y_continuous(breaks=number_ticks(6)) +
  theme_classic()
roc1_dis

roc1_til <- ggplot(data=conf_til_sti0, aes(x=prob0, y=prob1)) +
  geom_line() +
  geom_point() + labs(title="Fig.7 Type 1 ROC Tilt Recognition", x= "FAR", y="HR")+
  scale_x_continuous(breaks=number_ticks(6)) + scale_y_continuous(breaks=number_ticks(6)) +
  theme_classic()
roc1_til
```
&nbsp;

&nbsp;

&nbsp;

# 4.Type 2 ROC curves
```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=3.5, fig.height=3.5}
#Type 2 ROC preparation
###############
#  Detection  #
###############
#get incorrect trials 
conf_det0 <- subset(conf_det, accuracy=="0", select=c(confidence, response, prob_acc))
conf_det0 <- conf_det0[order(conf_det0[,1,2]),]
sex1 <- se(conf_det0$prob_acc)


#get incorrect trials with 1 response
confdet_incorrect1 <- conf_det0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="1")
confdet_incorrect1

#get incorrect trials with 0 response
confdet_incorrect0 <- conf_det0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="0")
confdet_incorrect0

#order df with descending confidence
confdet_incorrect0 <- confdet_incorrect0[order(-confdet_incorrect0$confidence),]
confdet_incorrect1 <- confdet_incorrect1[order(-confdet_incorrect1$confidence),]

#get cumulative prob
confdet_incorrect0[,'prob0']=cumsum(confdet_incorrect0[,'prob'])
confdet_incorrect1[,'prob0']=cumsum(confdet_incorrect1[,'prob'])

#bind incorrect trials together
confdet_incorrect <- rbind(confdet_incorrect0, confdet_incorrect1)

#get correct trials
conf_det1 <- subset(conf_det, accuracy=="1", select=c(confidence, response, prob_acc))
conf_det1 <- conf_det1[order(conf_det1[,1,2]),]
sey1 <- se(conf_det1$prob_acc)

#get correct trials with 1 response
confdet_correct1 <- conf_det1 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="1")
confdet_correct1 

#get correct trials with 0 response
confdet_correct0 <- conf_det1 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="0")
confdet_correct0

#order df with descending confidence
confdet_correct0 <- confdet_correct0[order(-confdet_correct0$confidence),]
confdet_correct1 <- confdet_correct1[order(-confdet_correct1$confidence),]

#get cumulative prob
confdet_correct0[,'prob1']=cumsum(confdet_correct0[,'prob'])
confdet_correct1[,'prob1']=cumsum(confdet_correct1[,'prob'])

#bind correct trials together
confdet_correct <- rbind(confdet_correct0, confdet_correct1)

#bind incorrect and correct trials together
confdet_acc <- inner_join(confdet_incorrect, confdet_correct, by=c("confidence", "response"))

#add the row for zero point for the ROC plot
confdet_acc <- ungroup(confdet_acc)

confdet_acc <- confdet_acc %>% add_row(confidence=7, response=0, prob_acc.x=0, prob.x=0, prob0=0, prob_acc.y=0, prob.y=0, prob1=0) %>% add_row(confidence=7, response=1, prob_acc.x=0, prob.x=0, prob0=0, prob_acc.y=0, prob.y=0, prob1=0)

#change response code
confdet_acc$response[confdet_acc$response=="0"] <- "No"
confdet_acc$response[confdet_acc$response=="1"] <- "Yes"

#calculating area under the curve
auc_detection <- t(sapply(split(confdet_acc, confdet_acc$response), function(x) {
  data.frame(response=x$response[1], auc=auc(x$prob0, x$prob1, type='spline'))
}))
AUC_det <- merge(confdet_acc, auc_detection)
AUC_det$auc <- as.numeric(AUC_det$auc)
auc_det <- AUC_det$'auc'
names(auc_det) <-AUC_det$response

#t test comparing area under the curve 
#det_auc<- (rnorm(no_subj, mean = unname(auc_det['No']), sd = sd_bias2))
#t.test(det_auc, mu = unname(auc_det['Yes'])) # 

#det_auc <- (rnorm(no_subj, mean = dis_bias, sd = sd_bias2))
#t.test(det_auc, mu = unname) # Ho: mu = 0.5

####################
#  Discrimination  #
####################
#get incorrect trials 
conf_dis0 <- subset(conf_dis, accuracy=="0", select=c(confidence, response, prob_acc))
conf_dis0 <- conf_dis0[order(conf_dis0[,1,2]),]

confdis_incorrect1 <- conf_dis0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="1")
confdis_incorrect1

confdis_incorrect0 <- conf_dis0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="0")
confdis_incorrect0

confdis_incorrect0 <- confdis_incorrect0[order(-confdis_incorrect0$confidence),]
confdis_incorrect1 <- confdis_incorrect1[order(-confdis_incorrect1$confidence),]

confdis_incorrect0[,'prob0']=cumsum(confdis_incorrect0[,'prob'])
confdis_incorrect1[,'prob0']=cumsum(confdis_incorrect1[,'prob'])

confdis_incorrect <- rbind(confdis_incorrect0, confdis_incorrect1)

conf_dis1 <- subset(conf_dis, accuracy=="1", select=c(confidence, response, prob_acc))
conf_dis1 <- conf_dis1[order(conf_dis1[,1,2]),]

confdis_correct1 <- conf_dis1 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="1")
confdis_correct1

confdis_correct0 <- conf_dis1 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="0")
confdis_correct0

confdis_correct0 <- confdis_correct0[order(-confdis_correct0$confidence),]
confdis_correct1 <- confdis_correct1[order(-confdis_correct1$confidence),]

confdis_correct0[,'prob1']=cumsum(confdis_correct0[,'prob'])
confdis_correct1[,'prob1']=cumsum(confdis_correct1[,'prob'])

confdis_correct <- rbind(confdis_correct0, confdis_correct1)
confdis_acc <- inner_join(confdis_incorrect, confdis_correct, by=c("confidence", "response"))
confdis_acc <- ungroup(confdis_acc)
confdis_acc <- confdis_acc %>% add_row(confidence=7, response=0, prob_acc.x=0, prob.x=0, prob0=0, prob_acc.y=0, prob.y=0, prob1=0) %>% add_row(confidence=7, response=1, prob_acc.x=0, prob.x=0, prob0=0, prob_acc.y=0, prob.y=0, prob1=0)
confdis_acc$response[confdis_acc$response=="0"] <- "Anticlockwise"
confdis_acc$response[confdis_acc$response=="1"] <- "Clockwise"

#Tilt recognition
conf_til0 <- subset(conf_til, accuracy=="0", select=c(confidence, response, prob_acc))
conf_til0 <- conf_til0[order(conf_til0[,1,2]),]

conftil_incorrect1 <- conf_til0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="1")
conftil_incorrect1

conftil_incorrect0 <- conf_til0 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="0")
conftil_incorrect0

conftil_incorrect0 <- conftil_incorrect0[order(-conftil_incorrect0$confidence),]
conftil_incorrect1 <- conftil_incorrect1[order(-conftil_incorrect1$confidence),]

conftil_incorrect0[,'prob0']=cumsum(conftil_incorrect0[,'prob'])
conftil_incorrect1[,'prob0']=cumsum(conftil_incorrect1[,'prob'])

conftil_incorrect <- rbind(conftil_incorrect0, conftil_incorrect1)

conf_til1 <- subset(conf_til, accuracy=="1", select=c(confidence, response, prob_acc))
conf_til1 <- conf_til1[order(conf_til1[,1,2]),]

conftil_correct1 <- conf_til1 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="1")
conftil_correct1

conftil_correct0 <- conf_til1 %>%
  group_by(confidence, response) %>%
  summarise_each(funs(sum)) %>%
  mutate(prob= prob_acc/no_subj) %>%
  filter(response=="0")
conftil_correct0

conftil_correct0 <- conftil_correct0[order(-conftil_correct0$confidence),]
conftil_correct1 <- conftil_correct1[order(-conftil_correct1$confidence),]

conftil_correct0[,'prob1']=cumsum(conftil_correct0[,'prob'])
conftil_correct1[,'prob1']=cumsum(conftil_correct1[,'prob'])
conftil_correct <- rbind(conftil_correct0, conftil_correct1)
conftil_acc <- inner_join(conftil_incorrect, conftil_correct, by=c("confidence", "response"))
conftil_acc <- ungroup(conftil_acc)
conftil_acc <- conftil_acc %>% add_row(confidence=7, response=0 ,prob_acc.x=0, prob.x=0, prob0=0, prob_acc.y=0, prob.y=0, prob1=0) %>% add_row(confidence=7, response=1 ,prob_acc.x=0, prob.x=0, prob0=0, prob_acc.y=0, prob.y=0, prob1=0)

conftil_acc$response[conftil_acc$response=="0"] <- "Vertical"
conftil_acc$response[conftil_acc$response=="1"] <- "Tilted"

#calculating area under the curve
auc_tilt <- t(sapply(split(conftil_acc, conftil_acc$response), function(x) {
  data.frame(response=x$response[1], auc=auc(x$prob0, x$prob1, type='spline'))
}))
AUC_til <- merge(conftil_acc, auc_tilt)
AUC_til$auc <- as.numeric(AUC_til$auc)
auc_til <- AUC_til$'auc'
names(auc_til) <-AUC_til$response

#################################### 
# Plotting type 2 ROC
####################################
roc2_det <- ggplot(data=confdet_acc, aes(x=prob0, y=prob1)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 4) + 
  scale_color_manual(values=c("#e41a1c", "#377eb8")) +
  labs(title="Fig.8 Type 2 ROC Detection", x= "p(conf | correct)", y="p(conf | incorrect)", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0, 1),breaks=number_ticks(6)) + scale_y_continuous(limits = c(0, 1), breaks=number_ticks(6)) +
  theme(legend.position=c(0.8, 0.2),  
                 legend.background = element_blank(),
        legend.title = element_blank(),
                 legend.key = element_blank(), 
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
roc2_det


roc2_dis <- ggplot(data=confdis_acc, aes(x=prob0, y=prob1)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 4) + 
  scale_color_manual(values=c("#984ea3", "#4daf4a")) +
  labs(title="Fig.9 Type 2 ROC Discrimination", x= "p(conf | correct)", y="p(conf | incorrect)", color="Response")+ 
  theme_classic() + scale_x_continuous(limits = c(0, 1),breaks=number_ticks(6)) + scale_y_continuous(limits = c(0, 1), breaks=number_ticks(6)) +
  theme(legend.position=c(0.8, 0.2),  
                 legend.background = element_blank(),
        legend.title = element_blank(),
                 legend.key = element_blank(),
        plot.title = (element_text(color = "black", size = 12, face = "italic")))
roc2_dis

roc2_til <- ggplot(data=conftil_acc, aes(x=prob0, y=prob1)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 4) + 
  scale_color_manual(values=c("#999999","#f781bf")) +
  labs(title="Fig.10 Type 2 ROC Tilt", x= "p(conf | correct)", y="p(conf | incorrect)", color="Response")+ 
  theme_classic()+ scale_x_continuous(limits = c(0, 1),breaks=number_ticks(6)) + scale_y_continuous(limits = c(0, 1), breaks=number_ticks(6)) +
  theme(legend.position=c(0.8, 0.2),  
                 legend.title = element_blank(),
        legend.background = element_blank(),
                 legend.key = element_blank(),
        plot.title = (element_text(color = "black", size = 12, face = "italic")))
roc2_til
```
&nbsp;

&nbsp;

Metacognitive sensitivity, which is quantified as the area under Type 2 ROC curve, is significantly higher for Yes (`r apa(unname(auc_det['Yes']), 2, T) `) than No (`r apa(unname(auc_det['No']), 2, T)`) response. Similar pattern is observed in the tilt recognition task, where the AUC is significantly higher for Tilted (`r apa(unname(auc_til['Tilted']), 2, T)`) than Vertical (`r apa(unname(auc_til['Vertical']), 2, T)`) responses. This suggest that participants confidence ratings are more diagnostic to accuracy in the judgments of a target stimulus being pressent than being absent. Similarly, the correct judgments of a stimulus being tilted is better reflected by partcipants' confidence ratings than the correct judgments of a stimulus being vertical. 

# 5.BOLD signal in ROIs

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=2.5, fig.height=3.2}
####################################
# BOLD data preparation detection 
####################################
Data_Det <- Data_Det %>%
  filter(! BOLD_rTPJ=="NaN")
Data_Det
Data_Det$response[Data_Det$response=="0"] <- "No"
Data_Det$response[Data_Det$response=="1"] <- "Yes"

#get the mean activation at each ROI for each participants at each confidence level for each response
BOLD_det_subj <- aggregate(Data_Det[, 16:21], list(Data_Det$subj_id, Data_Det$confidence, Data_Det$response, Data_Det$task ), mean)
#rename the colum names 
BOLD_det_subj <- rename(BOLD_det_subj,c('subj_id'='Group.1', 'confidence'='Group.2', 'response'='Group.3', 'task'='Group.4'))
#get the group mean of activation for each ROI
BOLD_det_mean <- aggregate(BOLD_det_subj[, 5:10], list(BOLD_det_subj$confidence, BOLD_det_subj$response), mean)
#get the se of activation for each ROI
BOLD_det_se <- aggregate(BOLD_det_subj[, 5:10], list(BOLD_det_subj$confidence, BOLD_det_subj$response ), se)
#combine with mean df==> ".x==mean, .y==se"
BOLD_det_mean <- inner_join(BOLD_det_mean, BOLD_det_se, by=c("Group.1", "Group.2"))
#rename the colum names 
BOLD_det_mean <- rename(BOLD_det_mean,c('confidence'='Group.1', 'response'='Group.2'))

######################################### 
# BOLD data preparation discrimination 
#########################################
Data_Dis <- Data_Dis %>%
  filter(! BOLD_rTPJ=="NaN")
Data_Dis
Data_Dis$response[Data_Dis$response=="0"] <- "Anticlockwise"
Data_Dis$response[Data_Dis$response=="1"] <- "Clockwise"

#get the mean activation at each ROI for each participants at each confidence level for each response
BOLD_dis_subj <- aggregate(Data_Dis[, 16:21], list(Data_Dis$subj_id, Data_Dis$confidence, Data_Dis$response, Data_Dis$task), mean)
#rename the colum names 
BOLD_dis_subj <- rename(BOLD_dis_subj,c('subj_id'='Group.1', 'confidence'='Group.2', 'response'='Group.3', 'task'='Group.4'))
#get the group mean of activation for each ROI
BOLD_dis_mean <- aggregate(BOLD_dis_subj[, 5:10], list(BOLD_dis_subj$confidence, BOLD_dis_subj$response ), mean)
#get the se of activation for each ROI
BOLD_dis_se <- aggregate(BOLD_dis_subj[, 5:10], list(BOLD_dis_subj$confidence, BOLD_dis_subj$response ), se)
#combine with mean df==> ".x==mean, .y==se"
BOLD_dis_mean <- inner_join(BOLD_dis_mean, BOLD_dis_se, by=c("Group.1", "Group.2"))
#rename the colum names 
BOLD_dis_mean <- rename(BOLD_dis_mean,c('confidence'='Group.1', 'response'='Group.2'))

#################################### 
# BOLD data preparation tilt 
####################################
Data_Til <- Data_Til %>%
  filter(! BOLD_rTPJ=="NaN")
Data_Til
Data_Til$response[Data_Til$response=="0"] <- "Vertical"
Data_Til$response[Data_Til$response=="1"] <- "Tilted"

#get the mean activation at each ROI for each participants at each confidence level for each response
BOLD_til_subj <- aggregate(Data_Til[, 16:21], list(Data_Til$subj_id, Data_Til$confidence, Data_Til$response, Data_Til$task ), mean)
#rename the colum names 
BOLD_til_subj <- rename(BOLD_til_subj,c('subj_id'='Group.1', 'confidence'='Group.2', 'response'='Group.3', 'task'='Group.4'))
#get the group mean of activation for each ROI
BOLD_til_mean <- aggregate(BOLD_til_subj[, 5:10], list(BOLD_til_subj$confidence, BOLD_til_subj$response ), mean)
#get the se of activation for each ROI
BOLD_til_se <- aggregate(BOLD_til_subj[, 5:10], list(BOLD_til_subj$confidence, BOLD_til_subj$response ), se)
#combine with mean df==> ".x==mean, .y==se"
BOLD_til_mean <- inner_join(BOLD_til_mean, BOLD_til_se, by=c("Group.1", "Group.2"))
#rename the colum names 
BOLD_til_mean <- rename(BOLD_til_mean,c('confidence'='Group.1', 'response'='Group.2'))
```

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=2.5, fig.height=3}
#################################### 
# Plotting rTPJ 
#################################### 
rTPJ_det <- ggplot(data=BOLD_det_mean, aes(x=confidence, y=BOLD_rTPJ.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_rTPJ.x-BOLD_rTPJ.y, ymax = BOLD_rTPJ.x+BOLD_rTPJ.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#e41a1c", "#377eb8")) +
  labs(title="rTPJ detection", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = element_blank(),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
rTPJ_det

rTPJ_dis <- ggplot(data=BOLD_dis_mean, aes(x=confidence, y=BOLD_rTPJ.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_rTPJ.x-BOLD_rTPJ.y, ymax = BOLD_rTPJ.x+BOLD_rTPJ.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#984ea3", "#4daf4a")) +
  labs(title="rTPJ discrimination", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.85, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = element_blank(),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
rTPJ_dis

rTPJ_til <- ggplot(data=BOLD_til_mean, aes(x=confidence, y=BOLD_rTPJ.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_rTPJ.x-BOLD_rTPJ.y, ymax = BOLD_rTPJ.x+BOLD_rTPJ.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#999999","#f781bf")) +
  labs(title="rTPJ tilt recognition", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.7, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = element_blank(),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
rTPJ_til
```
&nbsp;

&nbsp;

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=2.5, fig.height=3}
#################################### 
# Plotting vmPFC 
#################################### 
vmPFC_det <- ggplot(data=BOLD_det_mean, aes(x=confidence, y=BOLD_vmPFC.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_vmPFC.x-BOLD_vmPFC.y, ymax = BOLD_vmPFC.x+BOLD_vmPFC.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#e41a1c", "#377eb8")) +
  labs(title="vmPFC detection", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1.5, 0.5), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = element_blank(),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
vmPFC_det

vmPFC_dis <- ggplot(data=BOLD_dis_mean, aes(x=confidence, y=BOLD_vmPFC.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_vmPFC.x-BOLD_vmPFC.y, ymax = BOLD_vmPFC.x+BOLD_vmPFC.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#984ea3", "#4daf4a")) +
  labs(title="vmPFC detection", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1.5, 0.5), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = element_blank(),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
vmPFC_dis

vmPFC_til <- ggplot(data=BOLD_til_mean, aes(x=confidence, y=BOLD_vmPFC.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_vmPFC.x-BOLD_vmPFC.y, ymax = BOLD_vmPFC.x+BOLD_vmPFC.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#999999","#f781bf")) +
  labs(title="vmPFC detection", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1.5, 0.5), breaks=number_ticks(6))+
  theme(legend.position=c(0.7, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = element_blank(),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
vmPFC_til
```
&nbsp;

&nbsp;

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=2.5, fig.height=3}
#################################### 
# Plotting pMFC
#################################### 
pMFC_det <- ggplot(data=BOLD_det_mean, aes(x=confidence, y=BOLD_pMFC.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_pMFC.x-BOLD_pMFC.y, ymax = BOLD_pMFC.x+BOLD_pMFC.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#e41a1c", "#377eb8")) +
  labs(title="pMFC detection ", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(0.2, 1.8), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
pMFC_det

pMFC_dis <- ggplot(data=BOLD_dis_mean, aes(x=confidence, y=BOLD_pMFC.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_pMFC.x-BOLD_pMFC.y, ymax = BOLD_pMFC.x+BOLD_pMFC.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#984ea3", "#4daf4a")) +
  labs(title="pMFC discrimination", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(0.2, 1.8), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
pMFC_dis

pMFC_til <- ggplot(data=BOLD_til_mean, aes(x=confidence, y=BOLD_pMFC.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_pMFC.x-BOLD_pMFC.y, ymax = BOLD_pMFC.x+BOLD_pMFC.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#999999","#f781bf")) +
  labs(title="pMFC tilt", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(0.2, 1.8), breaks=number_ticks(6))+
  theme(legend.position=c(0.7, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
pMFC_til
```
&nbsp;

&nbsp;

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=2.5, fig.height=3}
#################################### 
# Plotting FPl
#################################### 
FPl_det <- ggplot(data=BOLD_det_mean, aes(x=confidence, y=BOLD_FPl.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_FPl.x-BOLD_FPl.y, ymax = BOLD_FPl.x+BOLD_FPl.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#e41a1c", "#377eb8")) +
  labs(title="FPl detection ", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-0.5, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
FPl_det

FPl_dis <- ggplot(data=BOLD_dis_mean, aes(x=confidence, y=BOLD_FPl.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_FPl.x-BOLD_FPl.y, ymax = BOLD_FPl.x+BOLD_FPl.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#984ea3", "#4daf4a")) +
  labs(title="FPl discrimination", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-0.5, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
FPl_dis

FPl_til <- ggplot(data=BOLD_til_mean, aes(x=confidence, y=BOLD_FPl.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_FPl.x-BOLD_FPl.y, ymax = BOLD_FPl.x+BOLD_FPl.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#999999","#f781bf")) +
  labs(title="FPl tilt", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-0.5, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.7, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
FPl_til
```
&nbsp;

&nbsp;

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=2.5, fig.height=3}
#################################### 
# Plotting FPm
#################################### 
FPm_det <- ggplot(data=BOLD_det_mean, aes(x=confidence, y=BOLD_FPm.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_FPm.x-BOLD_FPm.y, ymax = BOLD_FPm.x+BOLD_FPm.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#e41a1c", "#377eb8")) +
  labs(title="FPm detection ", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
FPm_det

FPm_dis <- ggplot(data=BOLD_dis_mean, aes(x=confidence, y=BOLD_FPm.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_FPm.x-BOLD_FPm.y, ymax = BOLD_FPm.x+BOLD_FPm.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#984ea3", "#4daf4a")) +
  labs(title="FPm discrimination", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.8, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
FPm_dis

FPm_til <- ggplot(data=BOLD_til_mean, aes(x=confidence, y=BOLD_FPm.x)) +
  geom_line(aes(colour = factor(response))) +
  geom_point(aes(color = factor(response)), size = 3) + 
  geom_errorbar( aes(ymin = BOLD_FPm.x-BOLD_FPm.y, ymax = BOLD_FPm.x+BOLD_FPm.y, colour = factor(response)), width = 0.1)+
  scale_color_manual(values=c("#999999","#f781bf")) +
  labs(title="FPm tilt", x= "confidence", y="mean activation", color="Response") +
  theme_classic() + scale_x_continuous(limits = c(0.5, 6),breaks=number_ticks(6)) + scale_y_continuous(limits = c(-1, 1), breaks=number_ticks(6))+
  theme(legend.position=c(0.7, 0.15),  
                 legend.background = element_blank(),
                 legend.key = element_blank(),
        legend.title = (element_text(size = 8)),
  legend.text = (element_text(size = 8)),
        plot.title = (element_text(color = "black", size = 12, face = "italic"))) 
FPm_til
```

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=2.5, fig.height=3}

BOLD_mean_subj <- rbind(BOLD_det_subj, BOLD_dis_subj, BOLD_til_subj)

#linear effect of conf (as continuous variables) on ROIs
lm_conf_vmPFC <- lm(formula = BOLD_vmPFC~confidence, data = BOLD_mean_subj)
lm_conf_pMFC <- lm(formula = BOLD_pMFC~confidence, data = BOLD_mean_subj)
lm_conf_rTPJ <- lm(formula = BOLD_rTPJ~confidence, data = BOLD_mean_subj)
lm_conf_FPl <- lm(formula = BOLD_FPl~confidence, data = BOLD_mean_subj)
lm_conf_FPm <- lm(formula = BOLD_FPm~confidence, data = BOLD_mean_subj)

#pull out beta and p values
b_lm_vmPFC <- coef(summary(lm_conf_vmPFC))[, "Estimate"]
b_lm_pMFC <- coef(summary(lm_conf_pMFC))[, "Estimate"]
b_lm_rTPJ <- coef(summary(lm_conf_rTPJ))[, "Estimate"]
b_lm_FPl <- coef(summary(lm_conf_FPl))[, "Estimate"]
b_lm_FPm <- coef(summary(lm_conf_FPm))[, "Estimate"]

p_lm_vmPFC <- coef(summary(lm_conf_vmPFC))[, "Pr(>|t|)"]
p_lm_pMFC <- coef(summary(lm_conf_pMFC))[, "Pr(>|t|)"]
p_lm_rTPJ <- coef(summary(lm_conf_rTPJ))[, "Pr(>|t|)"]
p_lm_FPl <- coef(summary(lm_conf_FPl))[, "Pr(>|t|)"]
p_lm_FPm <- coef(summary(lm_conf_FPm))[, "Pr(>|t|)"]

as.numeric(b_lm_vmPFC)
as.numeric(b_lm_pMFC)
as.numeric(b_lm_rTPJ)
as.numeric(b_lm_FPl)
as.numeric(b_lm_FPm)
as.numeric(p_lm_vmPFC)
as.numeric(p_lm_pMFC)
as.numeric(p_lm_rTPJ)
as.numeric(p_lm_FPl)
as.numeric(p_lm_FPm)

#lm with interactor task
lm_task_vmPFC <- lm(formula = BOLD_vmPFC~confidence+ confidence:task, data = BOLD_mean_subj)
lm_task_rTPJ <- lm(formula = BOLD_rTPJ~confidence+ confidence:task, data = BOLD_mean_subj)
lm_task_mPFC <- lm(formula = BOLD_pMFC~confidence+ confidence:task, data = BOLD_mean_subj)
lm_task_FPl <- lm(formula = BOLD_FPl~confidence+ confidence:task, data = BOLD_mean_subj)
lm_task_FPm <- lm(formula = BOLD_FPm~confidence+ confidence:task, data = BOLD_mean_subj)

#lm with interactor response detection
lm_resp_vmPFC <- lm(formula = BOLD_vmPFC~confidence+ confidence:response, data = BOLD_det_subj)
lm_resp_rTPJ <- lm(formula = BOLD_rTPJ~confidence+ confidence:response, data = BOLD_det_subj)
lm_resp_mPFC <- lm(formula = BOLD_pMFC~confidence+ confidence:response, data = BOLD_det_subj)
lm_resp_FPl <- lm(formula = BOLD_FPl~confidence+ confidence:response, data = BOLD_det_subj)
lm_resp_FPm <- lm(formula = BOLD_FPm~confidence+ confidence:response, data = BOLD_det_subj)

#lm with interactor response discrimination
lm_resp_vmPFC <- lm(formula = BOLD_vmPFC~confidence+ confidence:response, data = BOLD_dis_subj)
lm_resp_rTPJ <- lm(formula = BOLD_rTPJ~confidence+ confidence:response, data = BOLD_dis_subj)
lm_resp_mPFC <- lm(formula = BOLD_pMFC~confidence+ confidence:response, data = BOLD_dis_subj)
lm_resp_FPl <- lm(formula = BOLD_FPl~confidence+ confidence:response, data = BOLD_dis_subj)
lm_resp_FPm <- lm(formula = BOLD_FPm~confidence+ confidence:response, data = BOLD_dis_subj)

#lm with interactor response tilt
lm_resp_vmPFC <- lm(formula = BOLD_vmPFC~confidence+ confidence:response, data = BOLD_til_subj)
lm_resp_rTPJ <- lm(formula = BOLD_rTPJ~confidence+ confidence:response, data = BOLD_til_subj)
lm_resp_mPFC <- lm(formula = BOLD_pMFC~confidence+ confidence:response, data = BOLD_til_subj)
lm_resp_FPl <- lm(formula = BOLD_FPl~confidence+ confidence:response, data = BOLD_til_subj)
lm_resp_FPm <- lm(formula = BOLD_FPm~confidence+ confidence:response, data = BOLD_til_subj)

```
## Effect of confidence on BOLD signal in ROIs
From our data, negative linear confidence-related effects were observed in right Temporoparietal Junction (rTPJ) ($\beta$=`r apa(b_lm_rTPJ[2],2,T)`, p=`r apa(p_lm_rTPJ[2],3,T)`), Posterior Medial Frontal Cortex (pMFC)($\beta$=`r apa(b_lm_pMFC[2], 2,T)`, p=`r myround_p(apa(p_lm_pMFC[2], 3,T))`), as well as polsitive linear correlation between confidence and BOLD signals in Ventromedial Prefrontal Cortex (vmPFC)($\beta$=`r apa(b_lm_vmPFC[2],2,T)`, p=`r myround_p(apa(p_lm_vmPFC[2],3,T))`), Medial Frontopolar Cortex (FPm)($\beta$=`r apa(b_lm_FPm[2],2,T)`, p=`r apa(p_lm_FPm[2], 3,T)`). 

To investigate whether linear effects of confidence on BOLD signal were influenced by the type of task (Detection vs. Discrimination vs. Tilt recognition) and/or reponse (Yes vs. NO; Clockwise vs. Anticlockwise; Vertical vs. Tilted), linear models with interactions were tested. The effects of confidence failed to show a significant difference between three tasks in all ROIs (all p values > 0.23). No sognificant effect was observed between Yes and No response in detection (all p values > 0.11), between Clockwise and Anticlockwise responses in discrimination (all p values > 0.33) or between Vertical and Tilted responses in tilt recognition (all p values > 0.14).

```{r echo=FALSE, results = FALSE, message=FALSE, warning=FALSE, fig.width=2.5, fig.height=3}
#non-linear effect of conf and response (as categorical variables) on rTPJ
aov.resp_rTPJ_det <- aov(BOLD_rTPJ~response,data=BOLD_det_subj)
aov.conf_rTPJ_det <- aov(BOLD_rTPJ~confidence,data=BOLD_det_subj)

aov.resp_rTPJ_dis <- aov(BOLD_rTPJ~response,data=BOLD_dis_subj)
aov.conf_rTPJ_dis <- aov(BOLD_rTPJ~confidence,data=BOLD_dis_subj)

aov.resp_rTPJ_til <- aov(BOLD_rTPJ~response,data=BOLD_til_subj)
aov.conf_rTPJ_til <- aov(BOLD_rTPJ~confidence,data=BOLD_til_subj)

summary(aov.resp_rTPJ_det)
summary(aov.conf_rTPJ_det)
summary(aov.resp_rTPJ_dis)
summary(aov.conf_rTPJ_dis)
summary(aov.resp_rTPJ_til)
summary(aov.conf_rTPJ_til)

#effect of conf and response on vmPFC
```
&nbsp;

&nbsp;

## Citation 
[@denison2018pnasusa][@mazor2020e] 
&nbsp;

## Reference 
